Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-10 rnni_convexity.tex
sketch to fix the argument that csort gives a shortest path

The path $p$ returned by the algorithm $\csort$ is a shortest caterpillar path because every tree modification on $p$ reduces the number of inversions of taxa in $T$ and $R$.

>>>>

\begin{lemma}
$\csort(T, R)$ returns a shortest caterpillar path between $T$ and $R$.
\end{lemma}

\proof
Let $p$ be an arbitrary caterpillar path.
Every $\rnni$ move along $p$ can decrease the number of inversions of taxa in $T'$ and $R$ by either $1$ or $2$.
A decrease by $2$ is only possible when $T' = [x, y, z, \ldots]$, $z<\min(x,y)$, and the tree after the move is $[z, \min(x, y), \max(x, y), \ldots]$.
Hence $p$ is a shortest caterpillar path if every move along $p$ either is of this type or decreases the number of inversions by one.
Note that $\csort(T, R)$ satisfies this property.
\endproof
